A Continual Planner that Switches Between Serial and Decision-Theoretic Planning

### 2010-11-17 code/subarchitectures/planner.sa/trunk/src/latex/ICAPS-2011/moritz_2011.tex
Few small changes.
 -Charles

@@

@@

the effects of a sensing schema are perceptual, whereas the effects of
an operator schema are on the underlying state space.

@@

It can arise that in some propositional states an action is
applicable, and in others it is not. Moreover, a belief-state can
assign non-zero probability to states where that applicability holds,
and states where it does not. We forbid execution of actions that are
not applicable in any state of the current belief, and otherwise
suppose that when a non-applicable action is executed, that it has
no effect.

>>>>

Finally, we make a number of fairly standard assumptions. First, that
action execution and sensing occurs instantaneously, and that only one
action can be applied at a plan-step. Second, it can arise that in
some propositional states an action is applicable, and in others it is
not. Moreover, a belief-state can assign non-zero probability to
states where that applicability holds, and states where it does
not. We differ
from~\citeauthor{younes:littman:04}~\citeyear{younes:littman:04},
because we forbid the execution of actions that are not applicable in
any state of the current belief.  Also,
unlike~\citeauthor{hoffmann:brafman:2006}~\citeyear{hoffmann:brafman:2006},
we do incorporate a PPDDL-like default semantics, supposing that when
an action \stochAction\ is executed at some \bstate, that it has no
effect on states $\bstate(\state) > 0$ where $\poss(\stochAction)
\not\subseteq \state$.

@@

Goal expressions in the problem description ---for example
$(\pp{kval}~(\pp{location}~\pp{cornflakes}))$ expresses ``the robot
knows where the {\em cornflakes} are--- are treated as
control-knowledge by the planner. Here, CP is not allowed to start
executing a plan, unless in the finial stet the goal condition is
satisfied.

@@

The modelling language of choice for planning in probabilistic
problems is the Probabilistic Planning Domain Definition
Language~\cite{younes:littman:04}. PPDDL has been used to model
benchmarks in all 3 of the International Planning Competitions since
2004. A variation on PDDL for describing domains with stochastic
actions and uncertain starting configurations, PPDDL is a declarative
first-order (a.k.a., relational) that facilitates factored description
of domains and problem instances. There are straightforward
compilations from problems expressed compactly in PPDDL to
propositional representations amenable to state-of-the-art planning
procedures.  Because this language cannot model domains that feature
partial observability, for our setting we have developed DTPDDL, an
extension of PPDDL to partial observability.

For example, $(:\pp{predicates} (\pp{location} ?p - VisualObject))$
says that there is a unary predicate

the effects of a {\em sense} schema are perceptual, whereas the
effects of an {\em operator} schema are over state propositions.

@@
